Verifying Demonstrations

### 2018-08-13 paper/DB-anon-cred.tex
Minor clarification in DB-Schnorr

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmically with 
respect to the security parameter \(\lambda\) and repeat the protocol \(n\) 
times, such that the knowledge error, \((2^{-k})^n\), is small enough.
This will actually also decrease the success probability of the attacks 
presented below.

>>>>

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmically with 
respect to the security parameter \(\lambda\) and repeat the protocol \(n\) 
times, such that the knowledge error, \(2^{-kn}\), becomes small enough.
This is also needed to decrease the success probability of some of adversaries 
presented below.
